Inference of proto-neutron star properties from gravitational-wave data in core-collapse supernovae

### 2021-01-20 referee_answers.txt

We thank the refereee for his/her supportive comments and provide
answers below.

----------------------------------------------------------------------
Report of the Referee -- DY12631/Bizouard
----------------------------------------------------------------------

1. As far as I can tell, the model assumes that the GW signal is
dominated by g-modes originating from the PNS, which is consistent
with results reported from recent CCSN simulations from some groups.
However, other groups, using three-dimensional simulations, attribute
the dominant component to f- and g-modes (Radice et al. (2019), ApJL,
876, L9) or p- and g-modes (Mezzacappa et al. (2020), Phys. Rev. D,
102, 023027). Can the authors comment on this. In particular, discuss
the possible impact on model predictions if the signal is hybrid in
nature.

2. Most analysis of GW signals is based on two-dimensional models, and
the test set used in the present study is also comprised of 2D
simulations. Recent comparisons of signals from 2D and 3D simulations
show that the signal amplitude from 2D simulations is considerably
higher than in 3D simulations (e.g., Andresen et al. (2017), MNRAS,
468, 2032; see also Mezzacappa et al. 2020). I would like the authors
to comment on this, and its potential impact on the results presented
in the present paper. Would this just lower the upper limit of the
detectability distance? Are there other crucial differences between
signals from 2D and 3D simulations (e.g., the low frequency signal
from the spiral SASI mode) that could compromise the accuracy of the
model derived here? Please discuss this.

3. Are the 2D simulations new (i.e., computed for the present paper),
or have they been published elsewhere? If they have been published
elsewhere, please provide citation. Were any of the 2D simulations
constrained to spherical symmetry in the inner core to alleviate the
CFL condition? If so, could this restriction potentially suppress
modes that would otherwise have been excited by instabilities in the
PNS?

4. How do you define R_{PNS} in the 1D and 2D simulations? Is it the
radius for which the density achieves a specific value? Please clarify
this.

5. Can you elaborate on the motivation for the degrees of the
polynomials in Eqs. (1) and (2)? Why is r_i of degree 3 and log
sigma_i of degree 2?

A: We have tested several combinations using s20 waveform (up to degree
3 for both r_i and sigma_i) and have selected the best fitting model.

6. What do the red circles in Figure 1 represent? Is it a scatter plot
of the results from all 1D simulations taken together? Specifically,
since there obviously is more than 18 circles, how often is data from
each simulation sampled to generate the circles in Figure 1? Please
clarify this. Perhaps using a unique color for each model would help
clarify (but I do not demand this).

A: Each of the 18 1D simulations is providing data points r_i that are
plotted as function of f_i. Each simulation has between 100 and 300
points. All of them are plotted on Figure 1.

Should we make the plot with a color different for the 18 simulations?

### 2021-01-22 referee_answers.txt

3. Are the 2D simulations new (i.e., computed for the present paper),
or have they been published elsewhere? If they have been published
elsewhere, please provide citation. Were any of the 2D simulations
constrained to spherical symmetry in the inner core to alleviate the
CFL condition? If so, could this restriction potentially suppress
modes that would otherwise have been excited by instabilities in the
PNS?

4. How do you define R_{PNS} in the 1D and 2D simulations? Is it the
radius for which the density achieves a specific value? Please clarify
this.

5. Can you elaborate on the motivation for the degrees of the
polynomials in Eqs. (1) and (2)? Why is r_i of degree 3 and log
sigma_i of degree 2?

A: Figure 1 gives an idea of the relationship between frequencies and 
ratios, which is apparently quadratic.  However, we tested a bunch of 
models, namely, linear, quadratic, cubic, and some other combinations.  
We assessed their performance through the AIC criterion, getting the 
cubic as the best model. This is explained in our article.

About the model for log-sigma, we tested only 2 models: a linear and a 
quadratic. We found that the best model is the latter according to the AIC 
criterion.  Higher order models cause that the iterative fitting procedure 
does not converge in a satisfactory manner, which is warned by the authors 
of the lmvar package.

Figure 1 shows that overall the model (for r and log sigma) fits 
quite well the data set.

We have rewritten that paragraph to clarify this.

### 2021-01-22 methods.tex
model update
- Updating Figure 1 and caption
- Description of model selection
- Answer to Q5

\begin{figure}[t]
 \centering
 \includegraphics[width=0.45\textwidth]{plots/model}
 \caption{Ratio $M_{\rm PNS}/R_{\rm PNS}^2$ from our 18 1D simulations of the model set. The solid line is the maximum likelihood estimate of heteroscedastic cubic model with 95\% confidence bands (dashed lines) considering the 18 simulation data points.} 
 \label{fig:LMVAR}
\end{figure}

@@

The best fitting model amongst polynomials of degree 1, 2, and 3  was chosen according to
the Akaike information criterion with coefficients given in Table \ref{tab:model}, which is actually the model defined in \eqref{eq:model1}.  The data and fit of the model including 95\% confidence bands are displayed in
Figure~\ref{fig:LMVAR}.

>>>>

\begin{figure}[t]
 \centering
 \includegraphics[width=0.45\textwidth]{plots/model}
 \caption{Ratio $M_{\rm PNS}/R_{\rm PNS}^2$ from our 18 1D simulations of the model set. The solid line is the maximum likelihood estimate of heteroscedastic cubic model with 95\% confidence bands (dashed lines) considering the 18 simulation data points. \textcolor{red}{We have not made the distinction between the different simulations since we are only interested in the relationship between the variables.} }
 \label{fig:LMVAR}
\end{figure}

@@

\textcolor{red}{For the mean of the ratios $r_i$, the cubic model has the best fitting amongst polynomials of lower degrees, and for the mean of the log standard deviation $\log\sigma_i$, the quadratic model has the best fit compared to a polynomial of degree one.  The models were compared according to the Akaike information criterion.  The estimated coefficients are given in Table \ref{tab:model} and the data and fit of the final model including 95\% confidence bands are displayed in
Figure~\ref{fig:LMVAR}.}

%The best fitting model amongst polynomials of degree 1, 2, and 3  was chosen according to the Akaike information criterion with coefficients given in Table \ref{tab:model}, which is actually the model defined in \eqref{eq:model1}.  The data and fit of the model including 95\% confidence bands are displayed in Figure~\ref{fig:LMVAR}.
